---
title: "Organizing 2025 Fort Collins Classic music"
output: html_notebook
---


# Notes:

- A single person (Shelby 'Winter' Hutchinson) included a nickname in single quotes when they uploaded their music, so 
I removed those quotes in the music report and then moved the music file so it does not have single quotes in it.
- A parent sent me the correct music when finding they had uploaded the wrong one, so I have copied
`/gitignored_data/Swap-Out-Music/2025-FCC/SamerH.EP12526.1.mp3` into `gitignored_data/Music/2025FortCollinsClassic/PreliminaryEmotionalPerformance/Samer Hajibrahim7138_PDP_F.mp3`.
- Maria Julia Maymone had not gotten her music in.  (She was the only one, yay!)  She was out of the country,
apparently, and her coach, Christopher Darling sent it to me.  I put it first in
`MJ - Gimmie, Gimmie (PreJuv Excel FS 2_36).m4a' and from there I converted it to mp3 using the Music
app, and then saved the mp3 version to: `gitignored_data/Music/2025FortCollinsClassic/JuvenileGirlsExcel/Maria Julia Maymone4999_JGX_F.mp3`.
- I had to rename all the Synchro mp3 files to get them found by `associate_music_files()`
- I also had to fix an excess space in Ruthie and Nelia's music name:
```sh
/Adult16Duets/--% (main) mv Nelia\ Koontz\ \&\ Ruthie\ \ Lundin9632_ADT_F.mp3 Nelia\ Koontz\ \&\ Ruthie\ Lundin9632_ADT_F.mp3
```

## Scrape Start Order PDFs

```{r}
library(FCFSCmusicTools)

# we make a fix for a Van Pelt and another three-word name whose name does not get converted to report name correctly...
start_ords0 <- scrape_starting_orders("gitignored_data/2025-FCC-Starting-Orders") %>%
  mutate(
    report_name = case_when(
      music_name == "Gwenyth Van Pelt" ~ "Van Pelt, Gwenyth",
      music_name == "Ella Moon Owens" ~ "Moon Owens, Ella",
      music_name == "Rivkah Chavez Herrera" ~ "Chavez Herrera, Rivkah",
      report_name == "Koontz, Lundin &" ~ "Lundin, Ruthie",
      report_name == "Roybal, Rudman &" ~ "Rudman, Brynn",
      TRUE ~ report_name
    )
  )
```


## Read in the music report and clean it

```{r}
music_report0 <- read_excel("gitignored_data/FortCollinsClassic2025-MusicFile-2025-03-30_22-29.xls") %>%
  clean_music_report() %>%
  mutate(Name = str_replace_all(Name, "'", "")) # remove the single quotes around someone's name

synchro_music_report <- read_excel("gitignored_data/FortCollinsClassic2025-SYNCHRO-ONLY-MusicFile-2025-04-02_00_17.xls") %>%
  clean_music_report() %>%
  mutate(
    Name = str_replace_all(Name, "[^a-zA-Z ]", "") %>%
      str_replace_all(" +", " ")
  )

music_report <- bind_rows(music_report0, synchro_music_report)
```

Now, we do a little hand replacement to get the start_ords report_name for the synchro teams
to be OK:
```{r}
start_ords <- start_ords0 %>%
  mutate(
    report_name = case_when(
      report_name == "Icicles, Fort Collins Fire Crystal" ~ "Fort Collins Fire Crystals Icicles",
      report_name == "Fireflies, Fort Collins Fire Crystals -" ~ "Fort Collins Fire Crystals Fireflies",
      report_name == "Crystals, Fort Collins Fire" ~ "Fire Crystals",
      report_name == "Crystals, Fort Collins Adult Fire" ~ "Adult Fire Crystal Team", 
      TRUE ~ report_name
    )
  )
```

## Join those

```{r}
 joined <- join_report_and_start_order(
  MR = music_report,
  SO = start_ords
)

dir.create("gitignored_data/Outputs", showWarnings = FALSE, recursive = TRUE)

write_csv(joined, file = "gitignored_data/Outputs/2025-FCC-Inspect-And-Curate.csv")
```


## Filter and check the curated table


```{r}
filtered_events_list <- filter_and_check_curated_table("gitignored_data/Outputs/2025-FCC-Inspect-And-Curate-EDITED.csv")
```


## Associate the music with that all

```{r}
music_paths <- associate_music_files(
  C = filtered_events_list$clean,
  music_events_dir = "gitignored_data/Music/2025FortCollinsClassic",
  new_music_dir = "~/Desktop/StartOrderMusic---2025FortCollinsClassic"
)

# observe that there are no failures
music_paths$failures
```

Now let's rename all that music and put it on the Desktop.
Remove folder if still existing
```sh
rm -r ~/Desktop/StartOrderMusic---2025FortCollinsClassic
```
Then do it:
```r
result_of_copy <- copy_music_files(Tbl = music_paths$all_rows)
```

Then I checked the md5 checksums and they all looked good.

## Make a file of multi-event competitors

Sometimes people put their wrong music in for their different events.  In such cases
it is nice to know where their other pieces of music are.  I am going to make
a file of all the events for people in multiple events.
```{r}
music_paths$all_rows %>%
  select(Name, event_full)
```
