---
title: "2026 FoCo Classic Examples with Lacy"
output: html_notebook
---

Running through this whole thing using the 2025 FoCo Classic data, and then
ultimately also looking at some of the preliminary 2026 FoCo Classic data to
show Lacy how the package works.  

I am doing this on R version 4.5.2 which is a fairly virgin installation of
R (via conda) for my system so that I have to install the package, etc.
```r
remotes::install_github("eriqande/FCFSCmusicTools")
```
That failed so I tried getting the dependencies natively:
```r
install.packages(c('fuzzyjoin', 'pdftools', 'stringdist'))
```
Nope! That is probably a conda thing.  

So, I will try this all in the older native R that I am using...That worked
fine.  I suspect the native version has all the depedencies available as
binaries while the conda version does not.


We are using the data in `gitignored_data`.



## Scrape the start orders

```{r}
library(tidyverse)
library(FCFSCmusicTools)
library(readxl)

start_ords <- scrape_starting_orders("gitignored_data/2025-FCC-Starting-Orders")

```

The main purpose of this function is pull all the names and events of the starting orders
and then process them with a bunch of regular-expression parsing in order to transform the
names of the events and the names of the competitors into somethign that matches their
names from the EMS system in the music report and the event report.

This would all be easier if the events and competitor names were consistently reported
between the starting orders PDFs that Sheldrin makes and the reports and music that we
get from EMS!

The EMS report lists individuals as `Lastname, Firstname` while the starting order
PDFs list them as `Firstname Lastname, Skating_club`.  So the function `scrape_starting_orders()`
tries to parse that into `Lastname, Firstname`.  That goes into the column `report_name`.

The music comes from EMS sorted into event specific folders and then each piece named
`Firstname Lastname_` + `first4ofID#` + `_` + `F or S for short or freestyle` + `_` + `GroupNum` + `.mp3`.
So, the `music name` column in `start_ords` tries to get `Firstname Lastname`.

You can easily look at the `start_ords` data frame by doing `View(start_ords)` in RStudio.

When we look at that we can see the `_full` columns are the full data for each field
scraped out of the PDFs, and that got turned into the important columns for later use:

- `competitor_index`: starting place of the competitor
- `report_name`: best guess of what the competitor's name will be in the EMS report
- `music_name`: best guess of what the competitor's name will be in the music files
- `report_event`: best guess of what the event name will be in the EMS report

I say "best guess" because sometimes the name is a team name rather than individuals
in it, and sometimes people have two-part last names (like `Van Peters`) that screw
things up.


## Next step, get the music report from EMS 

I will make a video of how to download this music report as an excel file. For now,
we just use the one from 2025 for illustration.  We read it in and then run it through
the `clean_music_report()` function.  

Huge note here: the synchro is typically given in a separate report, so we need
to download each.  Read them both in, and the stack them one on top of the other
with the `bind_rows()` function.
```{r}
music_report_main <- read_excel("gitignored_data/FortCollinsClassic2025-MusicFile-2025-03-30_22-29.xls") %>%
  clean_music_report()

music_report_synchro <- read_excel("gitignored_data/FortCollinsClassic2025-SYNCHRO-ONLY-MusicFile-2025-04-02_00_17.xls") %>%
  clean_music_report()

music_report <- bind_rows(music_report_main, music_report_synchro)
```

We can look at that with `View(music_report)`.  

Now, the important thing to know is that we HOPE that the entries in the column
`Name` in the `music_report` will correspond to the entries in the column
`report_name` in the `start_ords`.

And likewise, we HOPE that the entries in the  `Event` column in the `music_report` 
will correspond to the entries int he column `report_event` in `start_ords`.

Again, we say "HOPE" because there may have been some parsing errors are three-part
name problems, etc.  But that is why we do some manual curation at this stage.
The function `join_report_and_start_order()` does a full join of the `start_ords`
and the `music_report` joining _only_ on `Name/report_name`.   We do this because
we often have discprepancies between the event names in the report and the start
orders and we will just manually curate those if needed.  

What it does do though, is calculate the string distance between the `report_event` in
`start_ords` and the `Event` in `music_report`.  If these are exactly the same, it
notes it as a perfect match and removes all other rows that joined up to it, so that
you don't have to deal with those during manual curation.  

**BIG NOTE! WE ARE JOINING ON  `music_name` NOW, AND KEEPING `Name` and `report_name`**


Let's see what this looks like:
```{r}
joined <- join_report_and_start_order(
  MR = music_report,
  SO = start_ords
)
```

We can look at `joined` like this `View(joined)`.

We see some `NA`s in `Event`.  This means that a row in the `start_ords` did not match up
via a name to a row in the `music_report`.  Likewise, if we see an `NA` in the `report_event`
column, that means that a row in the `music_report` did not join to anything in the
`start_ords`.  This often occurs when the competitor names between then start-order 
PDFs and the `music_report` are not well aligned.  

One way to see all of these issues and probably figure out what is going on is
by filtering `joined` to report only the rows that have NAs in Event or `report_event`
(and sort those by name).
```{r}
joined_nas <- joined %>%
  filter(is.na(Event) | is.na(report_event)) %>%
  arrange(Name)
```

Then do `View(joined_nas)`.  Aha!  We see the problem is that the `music_name` does
not match between start_ords and music_report.

If it has a `Name` the row came from the music_report.  If it has a `report_name` it came from
the start orders.  (By "has" i mean is not NA).


## Next step = manual curation

```{r}
write_csv(joined, file = "InspectAndCurate.csv")
```

Then immediately copy that to InspectAndCurate-EDITED.csv

Then do the `F` or `d` assignment in the STATUS column.

### Filter and check the curated table

Once the `d` and `F` notations have been made in the edited file (for example
`InsepctAndCurate-Edited.csv` in the example above) and those edits have been
saved in Excel (keeping it as a CSV file of the same name!!!) we read that back
into R and remove the rows marked `d`, then we break out the `F` rows into
a separate table `$follow_up` and a table of clean ones `$clean`.  The clean
ones are checked to make sure that there is exactly one entry for each
skater/music-report-event combo.

```{r}
filtered_events_list <- filter_and_check_curated_table("InspectAndCurate-Edited.csv")
```



### Associate the music files to these

We have a function to associate music files to the skater-event combos in a file
of mp3s that has been downloaded from EMS.

```{r}
music_paths <- associate_music_files(
  C = filtered_events_list$clean,
  music_events_dir = "gitignored_data/Music/2025FortCollinsClassic",
  new_music_dir = "~/Desktop/StartOrderMusic---2025FortCollinsClassic"
)
```


So, we have 327 pieces of music that work (and we have the Followups to deal with).

Now we can copy those into the `new_music_dir` directory that we specified above.

```{r}
result_of_copy <- copy_music_files(music_paths$all_rows)
```

Then check the md5s
```{r}
result_of_copy %>%
  filter(md5_orig != md5_new)
```
