---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FCFSCmusicTools

<!-- badges: start -->
<!-- badges: end -->

The goal of FCFSCmusicTools is to make it easy to copy the music for a figure
skating competition into a structure that follows the event order and start
order.

The basic ingredients it works with are:

1. The official Starting Order PDFs that are produced by Sheldrin.
2. The "Music Report" downloaded from EMS. (This is an excel file)
3. The directory full of directories full of music downloaded from EMS.



## Installation

You can install the development version of FCFSCmusicTools like so:

``` r
remotes::install_package("eriqande/FCFSCmusicTools")
```

## Example

Here I step through what I did for the 2024 Fort Collins Classic.  Unfortunately,
I can't post all the actual files on GitHub because it has individuals names
and ID numbers in it, etc.

```{r}
# load the library
library(FCFSCmusicTools)

```

### Scrape starting orders from Sheldrin's PDFs

Before we proceed, let's look at the files that we have from Sheldrin:
```
tree gitignored_data/2024-FCC-Starting-Orders/
gitignored_data/2024-FCC-Starting-Orders/
├── Friday
│   ├── 101ijs.pdf
│   ├── 102ijs.pdf
│   ├── 103ijs.pdf
│   ├── 104ijs.pdf
│   ├── 105ijs.pdf
│   ├── 106ijs.pdf
│   ├── 107ijs.pdf
│   ├── 108ijs.pdf
│   ├── 109ijs.pdf
│   ├── 110ijs.pdf
│   ├── 111ijs.pdf
│   ├── 112ijs.pdf
│   ├── 113ijs.pdf
│   ├── 114ijs.pdf
│   ├── 115ijs.pdf
│   ├── 116ijs.pdf
│   ├── 117ijs.pdf
│   ├── 118ijs.pdf
│   ├── 119ijs.pdf
│   ├── 120ijs.pdf
│   ├── 121ijs.pdf
│   ├── 122ijs.pdf
│   ├── 123ijs.pdf
│   ├── 124ijs.pdf
│   ├── 125ijs.pdf
│   ├── 126ijs.pdf
│   ├── 127.pdf
│   ├── 128.pdf
│   ├── 129.pdf
│   ├── 130.pdf
│   ├── 131.pdf
│   ├── 132.pdf
│   ├── 133.pdf
│   ├── 134.pdf
│   ├── 135.pdf
│   ├── 137.pdf
│   ├── 138ijs.pdf
│   ├── 139ijs.pdf
│   ├── 140ijs.pdf
│   ├── 141ijs.pdf
│   ├── 142ijs.pdf
│   ├── 144ijs.pdf
│   ├── 145ijs.pdf
│   ├── 146ijs.pdf
│   ├── 147ijs.pdf
│   ├── 148ijs.pdf
│   ├── 149ijs.pdf
│   ├── 150ijs.pdf
│   ├── 151.pdf
│   ├── 152.pdf
│   ├── 153ijs.pdf
│   └── 154ijs.pdf
├── Saturday
│   ├── 155ijs.pdf
│   ├── 156ijs.pdf
│   ├── 157ijs.pdf
│   ├── 158ijs.pdf
│   ├── 159ijs.pdf
│   ├── 160.pdf
│   ├── 161.pdf
│   ├── 162.pdf
│   ├── 163.pdf
│   ├── 164.pdf
│   ├── 165.pdf
│   ├── 166ijs.pdf
│   ├── 167ijs.pdf
│   ├── 168ijs.pdf
│   ├── 169ijs.pdf
│   ├── 170ijs.pdf
│   ├── 171ijs.pdf
│   ├── 172ijs.pdf
│   ├── 173ijs.pdf
│   ├── 174.pdf
│   ├── 175.pdf
│   ├── 176.pdf
│   ├── 177.pdf
│   ├── 178.pdf
│   ├── 179.pdf
│   ├── 180.pdf
│   ├── 181.pdf
│   ├── 182.pdf
│   ├── 183.pdf
│   ├── 184.pdf
│   ├── 185.pdf
│   ├── 186ijs.pdf
│   ├── 187ijs.pdf
│   ├── 188ijs.pdf
│   ├── 189ijs.pdf
│   ├── 190ijs.pdf
│   ├── 191ijs.pdf
│   ├── 192ijs.pdf
│   ├── 193ijs.pdf
│   ├── 194ijs.pdf
│   └── 195ijs.pdf
└── Sunday
    ├── 196.pdf
    ├── 197.pdf
    ├── 198.pdf
    ├── 199.pdf
    ├── 200.pdf
    ├── 201.pdf
    ├── 202.pdf
    ├── 203.pdf
    ├── 204.pdf
    ├── 205.pdf
    ├── 206.pdf
    ├── 207.pdf
    ├── 208.pdf
    ├── 209.pdf
    ├── 210.pdf
    ├── 211.pdf
    ├── 212.pdf
    ├── 213.pdf
    ├── 214.pdf
    ├── 215.pdf
    ├── 216.pdf
    └── 217.pdf

4 directories, 115 files
```

So, we want to get the relevant data out of those 115 PDF files.  We do that
with the function `scrape_starting_orders()`, like this:

```{r}
# scrape starting orders out of the files Sheldrin sent
start_ords <- scrape_starting_orders("gitignored_data/2024-FCC-Starting-Orders")
```

Here is what that looks like:
```{r}
start_ords
```

So, that is 370 separate starts, though not all will necessarily have music, that we are handling.   Cool...

### Read in the music report, join it, then manually inspect and curate the results

The Music Reports can be downloaded from the EMS.  Here we read one in and then we
run it though a quick function to fix situations where there are spaces before the commas
in the names (and/or no spaces after the comma).
```{r}
music_report <- read_excel("gitignored_data/2024FortCollinsClassic-MusicFile-2024-04-01 22·32.xls") %>%
  clean_music_report()
```

After that, we do a full join of the music report and the starting orders,
on the skater names using the function `join_report_and_start_order()`.
```{r}
joined <- join_report_and_start_order(
  MR = music_report,
  SO = start_ords
)
```

This join is done only on the skater names, because the event names might differ
in the starting orders compared to in the music report because:

1. Events of different levels may be merged in the starting orders.
2. There might be typos in the starting orders event names
3. I may not have cleaned up the starting order event names properly and there
   might be extra words in them.

This ends up being a many-to-many join, and at this point, the function checks
the event names from the records and the starting orders. If there is a starting-order
event (`report_event`) that perfectly matches a music-record event (`Event`), then
all other rows for that combination of skater name and music-record event are
filtered out by the function.  **(Note to Self: I could also filter out all occurrences
of `report_events` that perfectly match to the individual somewhere but which
have an imperfect match elsewhere.)**  The ones that remain are arranged in order of
string distance between the `Event` and the `report_event` and returned.  A first
column named `STATUS` of empty strings is added to this file as the first column.
This file should be saved as a csv and then some manual curation is required.  

```{r}
write_csv(joined, file = "InspectAndCurate.csv")
```

The CSV file should be copied to something new like `InsepctAndCurate-Edited.csv`
(this is so that your manual edits don't get overwritten by running the code above)
and opened (in Excel, for example) and the `STATUS` column
should be assigned values as follows:

1. No change if the row is correct and should stay.
2. `d` if the row should be dropped because the correct `report_event` is joined
   onto it elsewhere (typically right above the row that is getting a `d`). You can
   also use a `d` for any individuals that are in there with non-musical events
   that produce NA's in the Music Report columns (the ones with Capital Column names).
   Or if the skater+event corresponds to something that someone withdrew from.
3. `F` if the row needs follow-up for any number of reasons, for example:
    -  the skater name joined but there are
       no `event_reports` that correspond to the Event.  (Typically the skater has
       been placed into one or more non-music events (spin challenges, etc.) but the
       music report says the skater has some music).
    - There is a typo in the skater name either in the starting order or the
      music report (often spaces before the comma).
      


### Filter and check the curated table

Once the `d` and `F` notations have been made in the edited file (for example
`InsepctAndCurate-Edited.csv` in the example above) and those edits have been
saved in Excel (keeping it as a CSV file of the same name!!!) we read that back
into R and remove the rows marked `d`, then we break out the `F` rows into
a separate table `$follow_up` and a table of clean ones `$clean`.  The clean
ones are checked to make sure that there is exactly one entry for each
skater/music-report-event combo.

```{r}
filtered_events_list <- filter_and_check_curated_table("InspectAndCurate-Edited.csv")
```
The parsing issues here are not a concern for this data set.


### Associate the music files to these

We have a function to associate music files to the skater-event combos in a file
of mp3s that has been downloaded from EMS.
