---
title: "Processing Music For FrightFest 2025"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For FrightFest we use EntryEeze. I managed to get all turned around trying to login
as an admin.  Amy was able to reset the password for me, and I am in as `EricAFF2025`,
which must stand for Eric Admin Fright Fest 2025.  

Once logged in, I end up in the Admin Home site and then you can select the Music
tab, and Summary of Uploads under that.  There are 10 skaters still missing music.

After a flurry of emails. I got the needed music uploaded for almost everyone.

Some of the problems are duets where the partner uploaded the music. In some of those
cases I was able to download that music and upload it to the other partner so that it
does not show up as missing.  However, for Evangeline Singleton it shows up as her partner
having uploaded it, but it still shows her music as missing.  I just leave that.

The one person we need music for still is Alyssa Barrett.  But she will have to
get that into the mix on the day of the competition.

So, finally, on the music management tab I did the "Get spreadseet" button to get
"UploadsCompleted.csv" and I put that in the gitignored directory.

At this point I also downloaded all the music untagged, but I don't know yet
how the schedule is coming along (and whether sheldrin is making PDFs this year).

I have all the music in:
```
gitignored_data/FrightFest2025/Music/Sunday
```

They are named like this:
```
CompeteUSAProgramwMusic_Aspire2_Barrera_Frida.mp3
CompeteUSAProgramwMusic_Aspire2_Charoenying_Felicity.mp3
CompeteUSAProgramwMusic_Aspire2_Dally_Evelyn.mp3
CompeteUSAProgramwMusic_Aspire2_Gornell_Palmer.mp3
CompeteUSAProgramwMusic_Aspire2_Gould_Nora.mp3
CompeteUSAProgramwMusic_Aspire2_Hice_Bryleigh.mp3
```

There are only 194 pieces of music and it seems pretty straightforward.
I saw one accent on Cezanne that might give us some problems.

Gonna email Amy and see about the start orders....

## Doing it

So, the start orders will not be finished before I leave for the Southern Hemisphere.
Consequently I am going to just throw the music in event directories in alphabetical order
by skater.

This feels like it is going to be largely a one-off exercise. The ingredients are:
```{r}
library(tidyverse)
library(fs)
library(readxl)

# a tibble of music files paths and basenames
music_paths <- tibble(
  full_path = dir_ls("gitignored_data/FrightFest2025/Music/Sunday/")
) %>%
  mutate(
    basename = basename(full_path),
    basename = str_replace(basename, "\\.mp3$", "")
  ) %>%
  separate(
    basename, 
    into = c("event_camel", "level", "lastname", "firstname", "extra1", "extra2", "extra3", "extra4"),
    sep = "_",
    fill = "right"
    ) %>%
  mutate(
    firstname = replace_na(firstname, ""),
    extra1 = replace_na(extra1, ""),
    extra2 = replace_na(extra2, ""),
    extra3 = replace_na(extra3, ""),
    extra4 = replace_na(extra4, "")
  )
```

And then we need the actual schedule of things that they just finished.  People have been
calling this the 104.  I am going to keep the names of columns in lower case
for this one.
```{r}
the_104_sched <- read_excel(
  "gitignored_data/FrightFest2025/2025-Fright-Fest-final-draft-schedule.xlsx",
  sheet = 1,
  skip = 1
) %>%
  rename(
    event_num = `Event #`
  ) %>%
  mutate(event_num = as.integer(event_num)) %>%
  filter(!is.na(event_num)) %>%
  select(
    event_num,
    Event,
    Group,
    `Event Code`,
    `No. of Skaters`
  ) %>%
  rename(
    event = Event,
    group = Group,
    event_code = `Event Code`,
    number_of_skaters = `No. of Skaters`
  )
```

That is good.  Now, we basically need to associate each of those numbered events with
a numbered event from the `ScheduleSummaryEvents.csv` that I downloaded from EntryEeze,
because that has the names that correspond well with how the music is named.  We will make
the columns camel case here.
```{r}
SSE <- read_csv("gitignored_data/FrightFest2025/ScheduleSummaryEvents.csv") %>%
  rename(
    EventNum = `Event Num`,
    EventName = `Event Name`,
  ) %>%
  select(
    EventNum, EventName, Level, Group
  )
```

Great.  Now we want to join those to make sure that the schedule looks correct
(or at least that the event numbers match).
```{r}
compound_schedule <- the_104_sched %>%
  left_join(SSE, by = join_by(event_num == EventNum)) %>%
  filter(event_num >= 10)  # earlier events have no music
```

Then I looked at that to make sure things were lining up correctly.

It all checks out except for the SYS items:
```
Open Juv Synchro Exhibition
Open Masters Synchro Exhibition
```
I do not have music for those!!!

## Grouping the music

I should be able to squash (take out all special characters and spaces) the EventName
and Level, and get something that corresponds to the event name in the music titles.
And I am also going to make a column that gives the directory name which is from the
104 with dashes for spaces. And I am going to whittle the columns down to only what we
need, and we smoosh all groups together because we don't know who is in which
```{r}
compound2 <- compound_schedule %>%
  mutate(
    music_event_name = str_c(EventName, Level) %>% str_replace_all("[^a-zA-Z0-9]", ""),
    event_dir_name = str_replace_all(event, " ", "-")
  ) %>%
  select(event_num, number_of_skaters, event_dir_name, music_event_name) %>%
  group_by(event_dir_name, music_event_name) %>%
  summarise(
    number_of_skaters = sum(number_of_skaters),
    event_num = paste(event_num, collapse = ",", sep = "")
  ) %>%
  arrange(event_num)
```

And then I can clean up the music paths to have what we need
```{r}
music_paths2 <- music_paths %>%
  mutate(
    music_event_name = str_c(event_camel, level),
    file_name = str_c(lastname, "-", firstname, "-", extra1, extra2, extra3, extra4, "-", event_camel, "-", level, ".mp3")
  ) %>%
  select(music_event_name, file_name, full_path)
```

Now, I just full_join the compound2 and the music_paths2, and count up how many music files
are in each etc.
```{r}
full_set <- compound2 %>%
  full_join(music_paths2, by = join_by(music_event_name))
```


The first time I did that I found leftover music that revealed that:

- There was no number for Basic 5, so I added "16" to that
- It was missing a row for 11 Adaptive Aspire 2. I added that.

And now I continue by summarizing how many music files we have for each. 

```{r}
full_set2 <- full_set %>%
  group_by(music_event_name) %>%
  mutate(
    number_of_music_files = case_when(
      is.na(file_name) ~ 0L,
      TRUE ~ n()
    ),
    .after = number_of_skaters 
  )
```


And we can look at the missing music ones:
```{r}
mism <- full_set2 %>%
  filter(number_of_music_files != number_of_skaters) 

mism %>%
  write_csv("gitignored_data/FrightFest2025/skater-and-music-file-number-mismatches.csv")

mism
```

Problems I found and fixed there:

- Added Alyssa Barrett's music.
- Duplicated Duet music.  I deleted one of the versions.
- Lilia Behrle was missing music for `Showcase - Character Performance, Novice` and
  `Showcase - Lyrical Pop, Novice`.  I expect this is because she moved from intermediate
  to Novice.  (I got a late notice that her music was missing for novice from Entryeeze).
  She appeared as an extra unaccounted for skater in Intermediate, so I moved her intermediate music
  to Novice
- Same thing with Alexandra McNamara.  I moved her Intermediate Emotional Performance
  music to Novice
- Noelle Duncan, Had been signed up for PrePre Lyrical Pop and for `AdaptiveProgramwmusic_Aspire2_`
  but apparently she moved into different divisions.  So I moved her music to `Compete USA Program (w/Music), Basic 5`  and 
`Compete USA Showcase - Lyrical Pop, Basic 1 - 6`.  And then I remove the Adaptive Aspire 2


The only problems remaining are:

- missing music for some of the synchro teams
- 1 more music file than the number of skaters in `CompeteUSAProgramwMusicAspire3`
  and `CompeteUSAShowcaseLyricalPopAspire14`.
  
I just left those extra music files in, since we don't have start order anyway.


- Some had more music than skaters.  I just left those in there.



## Finally we are ready to copy music around

I am going to put the files we have into directories of event_num + event_dir_name. I can use the copy_music_files function.
```{r}
ready_for_copy <- full_set2 %>%
  ungroup() %>%
  filter(!is.na(full_path)) %>%
  arrange(event_num, file_name) %>%
  rename(
    orig_music_path = "full_path"
  ) %>%
  mutate(
    new_music_path = str_c(
      "/Users/eriq/Desktop/FrightFest2025--Music/", 
      event_num, "---", event_dir_name, "/", 
      file_name
    )
  )
```


Do it:
```{r}
check_it <- FCFSCmusicTools::copy_music_files(ready_for_copy)

# check the md5s
sum(check_it$md5_orig != check_it$md5_new)
```

