---
title: "Processing Music For FrightFest 2024"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For FrightFest we use EntryEeze, which has a different management system for Music.

Let's see if we can use the same tools for that (and probably write some new functions.)

The setup for what we are doing now is:

1.  Download all the music as _untagged_ and then put it in the gitignored directory.  It
    looks like this:
    ```{sh, eval=FALSE}
    gitignored_data/FrightFest2024/
    └── Music
     └── Sunday
        ├── AdultFreeSkate60_AdultPreBronze_Garg_Brenda.mp3
        ├── AdultFreeSkate60_AdultPreBronze_Hill_Barbra.mp3
        ├── CompeteUSAProgramwMusic_AdultHighBeginner_Koontz_Nelia.mp3
        ├── CompeteUSAProgramwMusic_AdultHighBeginner_Lundin_Ruthie.mp3
        ├── CompeteUSAProgramwMusic_Aspire1_Carrick_Grace.mp3
        ├── CompeteUSAProgramwMusic_Aspire1_Davis_Paige.mp3
     ...
    ```
    Note that I put it all in the "Sunday" folder.

2.  Download all of Shedrin's start order PDFs.  These are formatted slightly
    differently than at FoCo Classic last year, but I hope that they will still
    scrape out on the same lines. Here is what the files look like:
    ```{sh, eval=FALSE}
    gitignored_data/FrightFest2024/StartingOrders/
    └── Sunday
     ├── 105.pdf
     ├── 106.pdf
     ├── 107.pdf
     ├── 108.pdf
     ...
    ```
    


## Step 1. Scrape the starting orders

```{r}
library(FCFSCmusicTools)
library(tidyverse)


# scrape starting orders out of the files Sheldrin sent
start_ords <- scrape_starting_orders("gitignored_data/FrightFest2024/StartingOrders")

start_ords
```


OK, that parses out fine, it appears.

## Step 2: Get a tibble of music and paths

Because the event names are pretty munged between the music file names and the start orders,
and because there are only 139 pieces of music, or so, I think I will just associate
skater names (multiply, if there are multiple events) and then make a spreadsheet and hand-check
the correct ones.  
```{r}
music <- tibble(
    path = dir(path = "gitignored_data/FrightFest2024/Music/Sunday", full.names = TRUE)
  ) %>%
  mutate(
    basename = basename(path)
  ) %>%
  separate(basename, into = c("event", "level", "last", "first", "ext"))
```

Now, the music title have stripped all non-letters out of the things, so we will do the same with the
start orders, make a "squash_names" field that we can join on.
```{r}
so2 <- start_ords %>% 
  mutate(squash_name = str_replace_all(full_name, "[^a-zA-Z]", ""))

mus2 <- music %>%
  mutate(
    squash_name = case_when(
      is.na(ext) ~ str_replace_all(last, "[^a-zA-Z]", ""),
      TRUE ~ str_c(first, last) %>% str_replace_all("[^a-zA-Z]", ""),
    )
  )
```


Now, let's join those and get read to hand-check things.
```{r}
ready_for_eyes <- so2 %>%
  left_join(mus2, by = join_by(squash_name)) %>%
  arrange(squash_name, event_full) %>%
  group_by(squash_name) %>%
  mutate(
    music_event = event,
    music_level = level,
    keep_it = ifelse(n()==1, "x", ""),
    .after = event_full
  )

dir.create("gitignored_data/FrightFest2024/hand-check", recursive = TRUE, showWarnings = FALSE)
write_csv(ready_for_eyes, file = "gitignored_data/FrightFest2024/hand-check/hand-check-RAW.csv")

```


Then, I copy hand-check-RAW to hand-check-CHECKED.csv by hand, and then we can read that back in and
do some checks on it.
```{r}
hand_checked <- read_csv("gitignored_data/FrightFest2024/hand-check/hand-check-CHECKED.csv") %>%
  filter(keep_it == "x")


# how many keep_it events?  (139)
nrow(hand_checked)

# how many music titles?  (138)
nrow(music)

# We are missing Olivia's duet/trio music

# check to make sure that hand_checked music includes all that we have seen and no duplicates
setdiff(music$path, hand_checked$path.y)

# and what is the music we are missing there?
setdiff(hand_checked$path.y, music$path)

hand_checked %>%
  count(path.y) %>%
  count(n)

# yep! this is olivia's
hand_checked %>%
  filter(is.na(path.y))
```


Cool.  So, now all we have to do is choose a naming convention and copy the music over.
I am going to leave the name of the music file the same, but I will just add the
start order to the front of it.  That should be a good check that we have associated
the music correctly with each event.
```{r}
ready_to_copy <- hand_checked %>%
  filter(!is.na(path.y)) %>%
  mutate(
    new_music_path = file.path(
      "~/Desktop/StartOrderMusic---2024FrightFest", 
      day,
      str_replace_all(event_full, "/", "--"),   # remove forward slashes in the event names
      sprintf("%02d---%s", competitor_index, basename(path.y))
    ),
    orig_music_path = path.y,
    .before = day
  )
```

Then, we might want to remove the existing directory
```sh
rm -r ~/Desktop/StartOrderMusic---2024FrightFest
```

Then, run it:
```{r}
catch_it <- copy_music_files(ready_to_copy)
```

Let's check the MD5's:
```{r}
catch_it %>%
  count(md5_orig == md5_new)
```

That is good! We have 138 pieces of music correctly copied!

